Twists of supersymmetric gauge theories

### 2020-01-30 10draft.tex
10draft

\input ./combined_macros.sty

@@

\chris{As you pointed out, these lemmas should go with other discussion of functional analysis issues.}
\begin{lemma}[Free to Interacting Spectral Sequence] \label{free_int_ss_lemma}
Let $(E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.  There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
\end{lemma}
\begin{proof}
The BV complex is of the form $\left(\cO(\cE), Q + \{I,-\}\right)$.
We have already exhibited \brian{this is a general fact that should go in the functional analysis section} a differentiable pro-cochain complex structure on the BV complex via the 
natural decreasing filtration 
\[
F^k \cO (\cE) = \Sym^{\geq k} (\cE^\vee)
\]
which is compatible with both $Q$ and $\{I,-\}$ separately.
The associated graded of this filtration is the differentiable cochain complex given by
\[
\left(\prod_{n \geq 0} \Sym^n (\cE^\vee) , Q \right) .
\]
This is simply the BV complex associated to the free theory based on $(E, Q, \omega)$ obtained by forgetting $I$. 
Thus, the $E_1$ page of the corresponding spectral sequence is the BV cohomology of the underlying free theory, as desired. 
\brian{shall we say a word about convergence? This must follow from completeness of the filtration in addition to boundedness in some direction of the cohomology of $\cE$.} \chris{Does convergence require that the interaction is polynomial, or alternatively does this bound the number of differentials appearing in the spectral sequence?}
\end{proof}

\begin{lemma} \label{invert_quis_lemma}
Any quasi-isomorphism of cochain complexes admits a quasi-inverse.
\end{lemma}
\brian{I think Pavel had something to say for this lemma.}

@@

\chris{By the way, I see no obstruction to proving the following.  One just needs to check that the action of an infinitesimal symmetry $X$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.}
\begin{lemma}
If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
\end{lemma}

@@

The action functional for super Yang-Mills theory is given by
\[S(A,\lambda) = \int_{\RR^{n}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
where $\langle - \rangle_\fg$ denotes an invariant pairing on $\gg$, and where the latter term is obtained using the vector-valued pairing $\Gamma$ on $\Sigma$ to obtain a Dirac operator $\sd D_A \colon \Sigma \to \Sigma^*$. \chris{Brian suggested defining this notation in the section on supersymmety more broadly.  I agree.}

@@

\brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category? In any case, I do like that we've stated them clearly.} \chris{I'm not sure what you have in mind (for instance I'm not sure why you would need the Grothendieck condition there), but I think the lemmas below should be formally immediate in this dg category of differentiable cochain complexes setting (like the first one follows in any context where you have an exact sequence $0 \to A \to B \to C \to 0$ and the fact that if $C$ is equivalent to 0 then $A \to B$ is an equivalence, or the same with $A$ and $B \to C$.)}

@@

\begin{lemma} \label{interaction_pullback_lemma}
In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.  Suppose that all monomial summands of the interaction $I$ which depend on fields in $\mc C_2^\bullet$ also depend on fields in $\mc C_1^\bullet$. Then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
\end{lemma}

\begin{proof}
We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.  Because, by the hypothesis, all monomial summands of $I$ involving fields in $\mc C_2^\bullet$ also include fields in $\mc C_1^\bullet$, the pullback of $I$ under the map $F$ coincides with the pullback of $I$ under the inclusion map $\phi \mapsto (\phi, 0, 0)$ as required.
\end{proof}

@@

\begin{remark}
From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.  
This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading). 
As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
\end{remark}

@@

 \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.  The morphism from step 1 is just given by an inclusion, so the interaction on twisted 10d Yang-Mills theory is compatible with the interaction evaluated at $\chi'=\chi'^\vee=0$.  In order to make the same observation for the fields $\psi$ and $A_{1,0}$, we'll use Lemma \ref{interaction_pullback_lemma}, which we can apply using the observation that the antifields $A_{1,0}^\vee$ and $\psi^\vee$ only appear in the action together with the corresponding fields.  Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).  The resulting interaction is 
 \[
  I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
 \]
 which is, indeed, the interaction functional for holomorphic Chern-Simons theory.  The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.

@@

The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
\brian{How do we place 10d YM on an arbitrary 5-fold? 
Are you using something about sugra?
} \chris{Not an arbitrary 5-fold, but just Calabi-Yau.  I'm not thinking of using sugra.  Instead I want to say that a Calabi-Yau 5-fold has a principal $\SU(5)$ frame bundle.  Take the fields to be sections of the associated vector bundles under the appropriate representations, then use the same action functional: the Lagrangian density is $\SU(5)$ invariant and so will define a density on the 5-fold.}

>>>>

\input ./combined_macros.sty
\def\hCS{\mathrm{hCS}}

@@

\chris{As you pointed out, these lemmas should go with other discussion of functional analysis issues.}
\begin{lemma}[Free to Interacting Spectral Sequence] \label{free_int_ss_lemma}
Let $(\mc E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.  There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
\end{lemma}

\begin{lemma} \label{invert_quis_lemma}
Any quasi-isomorphism of cochain complexes admits a quasi-inverse.
\end{lemma}

@@

\chris{By the way, I see no obstruction to proving the following.}
\begin{lemma}
If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
\end{lemma}

@@

The action functional in 10d super Yang-Mills is given by
\[S(A,\lambda) = \int_{\RR^{n}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
where $\langle - \rangle_\fg$ denotes an invariant pairing on $\gg$, and where the latter term is obtained using the vector-valued pairing $\Gamma$ on $\Sigma$ to obtain a Dirac operator $\sd D_A \colon \Sigma \to \Sigma^*$. \chris{Brian suggested defining this notation in the section on supersymmety more broadly.  I agree.}

@@

@@

\begin{lemma} \label{interaction_pullback_lemma}
In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.  If $\mc C_2^\bullet = 0$, or if $\mc C_1^\bullet$ and $\mc C_2^\bullet$ are both isotropic subspaces of $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$, then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
\end{lemma}

@@

\begin{remark}
This twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.  As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $-1$-symplectic pairing.
\end{remark}

@@

 \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.  We'll use Lemma \ref{interaction_pullback_lemma}.  Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).  The resulting interaction is 
 \[
  I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
 \]
 which is, indeed, the interaction functional for holomorphic Chern-Simons theory.  The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.

@@

The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
